### 2016-08-05 notions.tex
writing up text for privacy notions

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a set-representation.
%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
%If $S$ has high min-entropy (element-wise), then it might still be
%possible to have security here.}\tsnote{I think we will always bump up
%against the (element-wise) min-entropy of the distribution over~$S$,
%at least in the ``one-wayness'' style definition that I had been imagining. }
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\pubaux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$. \tsnote{fixed by
  changing syntax.}\tsnote{Neither of these seems to capture the Neidermeier et al. attack.  Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}

@@

\tsnote{Is this the right kind of indistinguishability anyway?  This
  current notion says, in effect, that $S_0$ and $S_1$ are
  indistinguishable \emph{with respect to the allowed queries}
  (assuming that $\pubaux$ doesn't stupidly leak information.)  But
  why not try to formalize the intution that a representation~$M$ and
  the public info~$\pubaux$ tell you nothing (non-trivial) about the
  set being represented, period?  (Classical BFs, by the way,
  essentially leak the number of elements in the set by looking at the
  number of 0-bits in the array.)   That's tricky to define... I'll
  take a shot at it.}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}

>>>>

\subsection{Notions of Privacy}
One can also consider the orthogonal notion of privacy for a
set-representation.   There are various ways to formalize privacy, and
we give some of these in Figure~\ref{fig:privacy}.  
%\jnote{Actually, I am now unsure what the right way to define it is. It seems natural
%to give the attacker $\aux$. But if we give them $\aux$ and $M$ then they have everything.
%If $S$ has high min-entropy (element-wise), then it might still be
%possible to have security here.}\tsnote{I think we will always bump up
%against the (element-wise) min-entropy of the distribution over~$S$,
%at least in the ``one-wayness'' style definition that I had been imagining. }
On the left side of this figure, we give two ``one-wayness''
definitions, in which the adversary must output an element of the
set~$S$ represented by~$M$.  The first version (priv) gives the
adversary~$(M,\pubaux)$ as input; the second (wpriv) gives
only~$\pubaux$.  The wpriv-notion captures leakage about the elements
of~$S$ that results from observing the results of allowed queries.
The stronger priv-notion captures what is jointly leaked, by the
representation~$M$ and the allowed queries, about set elements.

On the right side of the figure, we give two ``indistinguishability''
notions of privacy.  The first version (ind-qry) captures more
generally what~$M$ and the allowed queries leak about the set that is
represented.  In particular, two sets~$S_0,S_1$ are sampled according
to distribution~$\distr{\calS}{}$, one of these is picked at random to
be represented.  The adversary is provided the resulting~$M,\pubaux$
and allowed to make queries~$q \in \calQ$; it must determine which
of~$S_0$ or~$S_1$ was actually represented.  We call this notion
indistinguishabilty (of sets) under a (adaptively chosen) query
attack.
%
The second version is inspired by the semantic security notion for
encryption schemes, and we refer to it as semantic-security (of sets)
with respect to the full representation (ss-rep).  In this experiment,
a set~$\calS$ is sample according to distribution~$\distr{\calS}{}$,
and the adversary is given the full ouput of running $\Rep(S)$,
i.e. $(M,\pubaux,\privaux)$.  The adversary must output a
function~$f\colon\calS \to \bits^*$ such that $f(S)$ differs from
$f(S')$ for a set~$S'$ that is subsequently sampled according to~$\distr{\calS}{}$.

\if{0}
There are several possible definitions:
\begin{enumerate}
\item A ``one-wayness'' definition where $S$ has high min-entropy (element-wise), and we
give the attacker $\pubaux$ and either $M$ or oracle access to $\Qry$. The attacker
succeeds if it can output an element in~$S$. \tsnote{fixed by
  changing syntax.}\tsnote{Neither of these seems to capture the Neidermeier et al. attack.  Giving the adversary~$M$ is closest, but our syntax would put the hash function secret keys into~$M$, which the Neidermeier attack doesn't get.}

@@

\tsnote{Is this the right kind of indistinguishability anyway?  This
  current notion says, in effect, that $S_0$ and $S_1$ are
  indistinguishable \emph{with respect to the allowed queries}
  (assuming that $\pubaux$ doesn't stupidly leak information.)  But
  why not try to formalize the intution that a representation~$M$ and
  the public info~$\pubaux$ tell you nothing (non-trivial) about the
  set being represented, period?  (Classical BFs, by the way,
  essentially leak the number of elements in the set by looking at the
  number of 0-bits in the array.)   That's tricky to define... I'll
  take a shot at it.}
%\tsnote{How will the adversary know that a query satisfies
%  this in (say) the case of the classical BF?  We can, of course,
%enforce it in the experiment, but then our resource accounting risks
%overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
%\tsnote{Also, we need that, in general, $\aux$ itself
%does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
%by the definition in this case.}
\end{enumerate}
\fi
